Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-01 sections/correlated-sicm-and-srfm.tex
Update correlated-sicm-and-srfm.tex

>>>>

As mentioned in section~\ref{sec:correlating-sicm-and-fm}, SICM was also successfully combined 
with dSTORM (see section~\ref{sec:smlm}) \cite{Hennig2015_nanoinj}. The difference to the 
SICM/STED microscopy correlation study was, that the SICM was in that study used for nanoinjecting 
fluorescently labeled molecules $-$ ATTO 655-phalloidin $-$ into living U2OS cells.

% Hier jetzt noch was zu SICM/SNOM!
